(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-09 table_fpp.tex
left-align
blah
fixing bold

\begin{deluxetable*}{lccccccc}

@@

 {\bf $201208431$ } & {\bf  $1$ } & {\bf  $0.51$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0058$ } & {\bf  $0.00011$ } & {\bf  $0.22$ } & {\bf  $0.0059$} \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\
 {\bf $201295312$ } & {\bf  $1$ } & {\bf  $0.04$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.008$ } & {\bf  $0.00014$ } & {\bf  $0.15$ } & {\bf  $0.0082$} \\
$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
 {\bf $201338508$ } & {\bf  $2$ } & {\bf  $0.33$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.17$ } & {\bf  $0.006$} \\
 {\bf $201367065$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.01$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.18$ } & {\bf  $0.01$} \\
 {\bf $201367065$ } & {\bf  $2$ } & {\bf  $0.67$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00063$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.14$ } & {\bf  $0.00063$} \\
 {\bf $201384232$ } & {\bf  $1$ } & {\bf  $0.44$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00017$ } & {\bf  $0.00023$ } & {\bf  $0.21$ } & {\bf  $0.0004$} \\
$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
 {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\

@@

 {\bf $201505350$ } & {\bf  $2$ } & {\bf  $0.70$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0025$ } & {\bf  $0.00013$ } & {\bf  $0.07$ } & {\bf  $0.0026$} \\
 {\bf $201546283$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.16$ } & {\bf  $< 10^{-4}$} \\
$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
 {\bf $201555883$ } & {\bf  $1$ } & {\bf  $0.94$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0044$ } & {\bf  $0.0004$ } & {\bf  $0.20$ } & {\bf  $0.0048$} \\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\

@@

 {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
 {\bf $201613023$ } & {\bf  $1$ } & {\bf  $0.08$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0016$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.15$ } & {\bf  $0.0016$} \\
$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
 {\bf $201629650$ } & {\bf  $1$ } & {\bf  $0.43$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.005$ } & {\bf  $0.0012$ } & {\bf  $0.17$ } & {\bf  $0.0062$} \\
$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\

@@

 {\bf $201736247$ } & {\bf  $1$ } & {\bf  $0.42$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0015$ } & {\bf  $0.00092$ } & {\bf  $0.22$ } & {\bf  $0.0024$} \\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\

@@

 {\bf $201855371$ } & {\bf  $1$ } & {\bf  $0.62$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.20$ } & {\bf  $0.00071$} \\
 {\bf $201912552$ } & {\bf  $1$ } & {\bf  $0.47$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00058$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.22$ } & {\bf  $0.00058$} \\
$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$

>>>>

\begin{deluxetable*}{lcllllll}

@@

 {\mathbf $201208431$ } & {\mathbf  $1$ } & {\mathbf  $0.51$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0058$ } & {\mathbf  $0.00011$ } & {\mathbf  $0.22$ } & {\mathbf  $0.0059$ \\
} & \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\
 {\mathbf $201295312$ } & {\mathbf  $1$ } & {\mathbf  $0.04$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.008$ } & {\mathbf  $0.00014$ } & {\mathbf  $0.15$ } & {\mathbf  $0.0082$ \\
} &$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
 {\mathbf $201338508$ } & {\mathbf  $2$ } & {\mathbf  $0.33$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.006$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.17$ } & {\mathbf  $0.006$ \\
} & {\mathbf $201367065$ } & {\mathbf  $1$ } & {\mathbf  $0.15$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.01$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.18$ } & {\mathbf  $0.01$ \\
} & {\mathbf $201367065$ } & {\mathbf  $2$ } & {\mathbf  $0.67$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00063$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.14$ } & {\mathbf  $0.00063$ \\
} & {\mathbf $201384232$ } & {\mathbf  $1$ } & {\mathbf  $0.44$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00017$ } & {\mathbf  $0.00023$ } & {\mathbf  $0.21$ } & {\mathbf  $0.0004$ \\
} &$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
 {\mathbf $201403446$ } & {\mathbf  $1$ } & {\mathbf  $0.18$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0069$ } & {\mathbf  $0.0013$ } & {\mathbf  $0.13$ } & {\mathbf  $0.0083$ \\
} &$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\

@@

 {\mathbf $201505350$ } & {\mathbf  $2$ } & {\mathbf  $0.70$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0025$ } & {\mathbf  $0.00013$ } & {\mathbf  $0.07$ } & {\mathbf  $0.0026$ \\
} & {\mathbf $201546283$ } & {\mathbf  $1$ } & {\mathbf  $0.15$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.16$ } & {\mathbf  $< 10^{-4}$ \\
} &$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
 {\mathbf $201555883$ } & {\mathbf  $1$ } & {\mathbf  $0.94$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0044$ } & {\mathbf  $0.0004$ } & {\mathbf  $0.20$ } & {\mathbf  $0.0048$ \\
} & \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\

@@

 {\mathbf $201577035$ } & {\mathbf  $1$ } & {\mathbf  $0.14$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00015$ } & {\mathbf  $0.20$ } & {\mathbf  $0.0002$ \\
} &$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
 {\mathbf $201613023$ } & {\mathbf  $1$ } & {\mathbf  $0.08$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0016$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.15$ } & {\mathbf  $0.0016$ \\
} &$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
 {\mathbf $201629650$ } & {\mathbf  $1$ } & {\mathbf  $0.43$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.005$ } & {\mathbf  $0.0012$ } & {\mathbf  $0.17$ } & {\mathbf  $0.0062$ \\
} &$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\

@@

 {\mathbf $201736247$ } & {\mathbf  $1$ } & {\mathbf  $0.42$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0015$ } & {\mathbf  $0.00092$ } & {\mathbf  $0.22$ } & {\mathbf  $0.0024$ \\
} &$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\

@@

 {\mathbf $201855371$ } & {\mathbf  $1$ } & {\mathbf  $0.62$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0006$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.20$ } & {\mathbf  $0.00071$ \\
} & {\mathbf $201912552$ } & {\mathbf  $1$ } & {\mathbf  $0.47$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00058$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.22$ } & {\mathbf  $0.00058$ \\
} &$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$
